#My 1st Knit Project

```{r,echo=FALSE}
#general options
options(scipen=999)

```
##Loading and preprocessing the data

This is the code for preprocessing the data 

```{r}
setwd("/Users/AmirKh/Documents/R/Reproducible Research/project1")
activity <- unzip("repdata-data-activity.zip")
act<-read.csv(activity)
rm(activity)
act<- as.data.frame(act)
```

##What is mean total number of steps taken per day?

First, We calculate the total number of steps taken per day :
```{r}
act.sum <- aggregate(x =act[c("steps")],
                     FUN = sum,
                     by = list(Group.date = act$date))
act.sum<-act.sum[is.na(act.sum$steps)==FALSE,]
```

histogram of the total number of steps taken each day :
```{r, echo=FALSE}
hist(act.sum$steps,xlab="Total number of steps taken each day",main="Histogram of the total steps taken each day")
```
```{r, echo=FALSE}
steps_mean<-mean(act.sum$steps)
steps_median<-median(act.sum$steps)
```
the mean of the total number of steps taken per day is `r steps_mean`.
the median of the total number of steps taken per day is `r steps_median`.

##What is the average daily activity pattern?
this is plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r, echo=FALSE}
act_avg<-aggregate(steps ~ interval, act, mean)
with(act_avg, plot(interval,steps,type='l'))
max_num<- act_avg$interval[which(act_avg$steps==max(act_avg$steps))]

```
 
the 5-minute interval, on average across all the days in the dataset, that contains the maximum number of steps is `r max_num`


## Imputing missing values


```{r,echo=FALSE}
NA.sum<-sum(is.na(act))
```
the total number of missing values in the dataset is `r NA.sum`

Imputing mean steps by interval code :
```{r}
act_full<-merge(act,act_avg,all.x=TRUE,by="interval")

for (i in 1:dim(act_full)[1]) {
        if ( is.na(act_full$steps.x[i]) )  {
                
                act_full$steps.x[i]<-act_full$steps.y[i]
        }
}
names(act_full)[2]<-"steps"
act_full<-act_full[,-4]             


act_full.sum <- aggregate(x =act_full[c("steps")],
                     FUN = sum,
                     by = list(Group.date = act_full$date))
act_full.sum<-act_full.sum[is.na(act_full.sum$steps)==FALSE,]

```

here is a histogram of the total number of steps taken each day

```{r, echo=FALSE}
hist(act_full.sum$steps,xlab="Total number of steps taken each day",main="Histogram of the total steps taken each day")        
mean_full<-mean(act_full.sum$steps)
median_full<-median(act_full.sum$steps)

```



after the imputing :
the mean of total number of steps taken per day is `r mean_full`
the median of total number of steps taken per day is `r median_full`

##Are there differences in activity patterns between weekdays and weekends?

the plot below shows the differences in activity patterns between weekdays and weekends
```{r,echo=FALSE}
library(ggplot2) 
act_full$date<-as.Date(act_full$date)
act_full$wk_end<-as.factor(weekdays(act_full$date) %in% c("Saturday","Sunday"))
act_full$wk_end<-factor(act_full$wk_end,labels=c("Weekday","Weekend"))

act_full_avg<-aggregate(steps ~ interval+wk_end, act_full, mean)
k <- ggplot(act_full_avg, aes(interval, steps)) +geom_line()
k + facet_grid(. ~ wk_end)
```
